\documentclass{nk-resume}
\usepackage{color}
\usepackage{setspace}
\usepackage{hyperref}

\begin{document}

\pagenumbering{gobble}

%%%%%%%%%%%%%%%%%%%%%%%% RESUME TEXT %%%%%%%%%%%%%%%%%%%%%%%%

\textsc{\huge{Nikita Khomitsevych}}

\vspace*{14px}

\href{mailto:hamsternik9@gmail.com}{hamsternik9@gmail.com} 

\href{https://hamsterniknotes.com}{www.hamsterniknotes.com}

\href{http://github.com/hamsternik}{\normalsize{GitHub}}
\hspace{2px}
\href{https://stackoverflow.com/users/3527499/hamsternik}{\normalsize{Stack Overflow}}
\hspace{2px}
\href{https://www.linkedin.com/in/khomitsevych/}{\normalsize{LinkedIn}} 

\vspace*{14px}

Mobile (iOS) and web frontend software engineer with 7 years of production experience in plenty of complex projects 
and distributed software development teams. Worked on projects targeting both B2C market and B2B area 
(sometimes strictly related to the hardware manufactor). Have relative work experience in either of 
outsource / outstaff / product companies covering specific circumstances related to each of them. 
Although the main area I have been worked is iOS-specified there are bunch of technologies and tools I've been worked within.
Describe myself as \href{https://alexkondov.com/the-t-shaped-engineer/}{T-Shaped Engineer}.

%%%%%%%%%%% Personal projects section

\subsection*{Recent Projects}

[RU] \textbf{\href{https://robotdreams.cc/course/ios-razrabotka-prilozheniy-s-0}{iOS From Scratch Course}}, 2021/02--2021/05.
\newline Lecturer and course creator (Part-time). Project: \href{https://github.com/hamsternik/robotdreams-ios-course}{GitHub course repository}.
\newline The course contains 20 lectures and the final assessment described requirements to follow and suggested theme to implement.
Course aims to cover multiple topics necessary for iOS developer:
Swift basics (e.g. variables, types, functions, classes, protocols etc), iOS frameworks (UIKit, Core Animation), 
memory management, concurrency (GCD), key-value data storage, network, development tools etc.
\newline The goal of the course was to prepare students without computer science degree or any programming skills to the \textit{junior iOS developer} job position.

%%%%%%%%%%% Recent Employments section

\subsection*{Recent Employments}

\textbf{\href{https://www.fluxon.com/}{Fluxon}}, 2022/06--2022/11.
Software engineer.
\newline Worked on two web applications, dealing with the front-end part either of the project.
Studied web tech stack, e.g TypeScript, React.js, Next.js, Firebase, Cloud Firestore.
\newline Developed (was solo developer) macOS application to remind about the upcoming meeting 
in your Google calendar, blasting upfront on your screen. The project was developed from scratch and 
was inspired by the \href{https://github.com/leits/MeetingBar}{MeetingBar} tool.
Technologies inluded Swift, SwiftUI, AppKit, Combine and XCTests.

\vspace*{14px}

\textbf{\href{https://www.life360.com}{Life360 Inc.}}, 2020/01--2022/04. 
Senior iOS Engineer (Contractor).
\newline Worked on major product parts of the Life360 iOS application 
(30+ million MAU, end of Q1 2022). Developed Family Safety Assist (FSA) feature allowing access 
e.g. roadside assistance in US and Canada. Developed Lead Generation feature to provide specific offers 
for customers from auto insurance companies. Led a team at 4 mobile developers (Android and iOS), 
tackling requirements processing, delivery responsibilities and people management. Developed user's 
driving experience workflow, created brand new tab ‘Driving’ including weekly driver report 
to see driving statistics and promote safe driving.\newline
Technologies included Swift, UIKit, RxSwift, Uber RIBs, XCTests, Fastlane etc.

\vspace*{14px}

\textbf{\href{https://betterme.world/about}{BetterMe USA}}, 2018/11--2019/12. 
iOS Software Engineer (Full-time).
\newline Developed a number of fast-growing Health \& Fitness apps in the world, 
aimed to improve people’s fitness level and general health status. Developed and supported 
\href{https://www.raywenderlich.com/books/advanced-ios-app-architecture/v3.0/chapters/6-architecture-redux}{Redux architecture} 
on most of our apps. Developed brand new version of 'BetterMe: Weight Loss Workouts' iOS application 
getting away from VIPER to the Redux. Supported custom Jenkins pipeline as mandatory CI/CD delivery platform. 
Developed bunch of Ruby scripts using Fastlane as a primary tool for a daily work tasks automatization.
\newline Top-3 applications with my contribution: 
\href{https://apps.apple.com/us/app/betterme-weight-loss-workouts/id1264546236}{BetterMe: Weight Loss Workouts}, 
\href{https://apps.apple.com/us/app/betterme-calm-sleep-meditate/id1363010081}{BetterMe: Calm, Sleep, Meditate}, 
\href{https://apps.apple.com/us/app/betterme-walking-weightloss/id1434400695}{BetterMe: Walking \& Weightloss}

\vspace*{14px}

\textbf{\href{https://www.cybervisiontech.com}{CyberVision, Inc.}}, 2016/04–-2018/09.
\newline Mobile Software Engineer (Full-time). Project: \href{https://www.nuvocares.com/solutions}{Nuvo: applications for pregnant and doctor}.
\newline Worked on iOS applications for manufactored FDA cleared device for remote nonstress tests for pregnant. 
iOS application was intended to monitor real-time health indicators of a pregnant woman and her fetus. 
Developed both applications for pregnant and doctor on iPhone and iPad.
Architectured and developed a separated SDK to deal with device via Bluetooth Classic.
Supported FDA and MFi device certification from engineering side.
\newline Technologies included Swift, UIKit, CoreGraphics, SwftCharts, VIPER architecture, 
Bluetooth Classic, Alamofire, RxSwift, Swinject. Used Nimble, Quick and Cuckoo tools leaning on BDD approach.

\vspace*{7px}

iOS Software Engineer (Full-time). Project: \href{https://www.sensynehealth.com/cleanspace}{CleanSpace application}.
\newline Worked on iOS SDK for CleanSpace application. 
Provided a full cycle of application development, inclduing architecture planning, 
development cycle and end-to-end testing.
Developed third-party frameworks from scratch for next integration on the iOS application.
Created Objective-C library that enables communication with BLE peripheral.
Created Swift library implemented iBeacon communication workflow. 
\newline Technologies included Swift, UIKit, Autolayout, CoreGraphics, CoreBluetooth, CoreLocation, Alamofire, PromiseKit.

%%%%%%%%%%% Education section

\subsection*{Education}

\begin{samepage}
Master's Degree in Computer Science, 2017--2018.
\newline \href{https://kpi.ua/en}{Igor Sikorsky Kyiv Polytechnic Institute (KPI)}, Faculty of Biomedical Engineering.

\vspace*{7px}

Bachelor's Degree in Computer Science, 2013--2017.
\newline \href{https://kpi.ua/en}{Igor Sikorsky Kyiv Polytechnic Institute (KPI)}, Faculty of Biomedical Engineering.
\end{samepage}

\end{document}